Motor Learning Without Moving

### 2018-08-07 ManuscriptMaterials.Rmd
More updates to reflect what is in the manuscript better.

First we load those other scripts:

@@

And we try to import some packages we use here:

@@

@@

```{r requireChiSquared_packages}
required.packages = c('nlme', 'car')
installRequire.Packages(required.packages, installmissing=FALSE)
```

@@

Since participants trained with a single target, we could look at generalization curves. These appear to be shifted more counter clockwise in most cases, so we want to quantify this. But, for most of the curves, and especially the ones that seems to be shifted, we don't have data on the full curve on one side of the peak. Or maybe it doesn't even include the peak itself. That makes it hard to fit a normal function to the data. Instead, we assume that the minimal change in the data, occurs far beyond the boundaries of the measured workspace, make the data cumulative and scale back to a range from 0 to 1. This allows fitting a _cumulative_ normal function where the 50% point corresponds to the peak of the generalization curve. This method is more stable, and actually works on all the datasets used (but we didn't test online localization from the classic experiment). However, the results should still be considered carefully.

@@

```{r load_select_participantInfo}
participants <- load.DownloadDataframe(informationURLs['demographics'],'participants_exposure.csv')
if (selectPerformance) {
  participants <- participants[which(participants$participant %in% OKparticipants),]
}
```

@@

```{r age_stats}
print(c('mean'=mean(participants$age), 'sd'=sd(participants$age)))
```

@@

```{r sex_distribution}
print(table(participants$sex))
```

@@

```{r fig3_localization, fig.width=7.5, fig.height=2.5}
plotLocalization(classicOnline=TRUE, selectPerformance=selectPerformance)
```

@@

```{r localization_count_table}
kable(getLocCountTable(selectPerformance=selectPerformance))
```

@@

```{r fig2_reachaftereffect, fig.width=7.5, fig.height=2.5}
plotReachAftereffects(selectPerformance=FALSE)
```

@@

So there is no effect of iteration here, nor does it interact with target, which means the reach aftereffects are the same for the first iteration and the average across the other four iterations. We now also see an effect of target angle: the generalization curve is not flat. This seems mostly due to the extra training.

@@

```{r create_svgs, cache=FALSE, include=FALSE}
# This chunk creates SVG files but shouldn't show up in the PDF / HTML 
plotReachAftereffects(generateSVG=TRUE,
                      selectPerformance=selectPerformance)
plotLocalization(classicOnline=TRUE,
                 generateSVG=TRUE, 
                 selectPerformance=selectPerformance)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE, 
                                               selectPerformance=selectPerformance)
```

>>>>

We load those other scripts:

@@

## Packages

We try to import some packages used here. This has already been attempted by `shared.R` (for people without R Studio), but in the chunk below we can easily take action if the required packages are not available on the current system.

@@

**If this fails: set the `installmissing` argument to TRUE to install the packages.**

@@

```{r requireChiSquared_packages}
if (LMEmethod=='chi-squared') {
  required.packages = c('nlme', 'car')
  installRequire.Packages(required.packages, installmissing=FALSE)
}
```

@@

Since participants trained with a single target, we could look at generalization curves. These appear to be shifted more counter clockwise in most cases, so we want to quantify this. But, for most of the curves, and especially the ones that seems to be shifted, we don't have data on the full curve on one side of the peak. We can still bootstrap the __peak__ of Guassian functions fit to the data across many samples of participants for the exposure group and for the delayed localization after classic training, but not for the online localization after classic training. This data is presented in the paper, where we only look at the peak of the localization -- not the width of the generalization curve.

The range of the data doesn't include the peak in many cases, which makes it hard to fit a normal function to the data. In one alternative approach, we assume that the minimal change in the data, occurs far beyond the boundaries of the measured workspace, make the data cumulative and scale back to a range from 0 to 1. This allows fitting a _cumulative_ normal function where the 50% point corresponds to the peak of the generalization curve. This method is more stable, and seems to works fairly well on the datasets where the more common fits also work (but we didn't test online localization from the classic experiment). Code for this approach is available (functions `psychometricGeneralization()`, `pnormMSE()` and `getCDFpeaks()` at the end of the file: `shared.R`), but the results are not presented in the paper or notebook.

@@

```{r load_select_participantInfo}
participants <- load.DownloadDataframe(informationURLs['demographics'],
                                       'participants_exposure.csv')

if (selectPerformance) {
  participants <- participants[which(participants$participant %in% OKparticipants),]
}
```

@@

```{r age_stats}
kable( c('mean'=mean(participants$age), 'sd'=sd(participants$age)),
       col.names=c('age'),
       caption='age of participants')
```

@@

```{r sex_distribution}
kable( table(participants$sex),
       caption='sex of participants',
       col.names=c('sex','frequency'))
```

## Localization selection statistics

We've manually selected localization responses that were unlikely to be true responses. Here are the statistics on how many were removed in each dataset. For exposure:

```{r exposure_loc_selection}
kable( aggregate(trials ~ rotated * passive, 
                 data=countSelectedLocalizations('exposure'), 
                 FUN=mean), 
       caption='percentages selected localization trials after exposure training')
```

For classic:

```{r classic_loc_selection}
kable( aggregate(trials ~ rotated * passive,
                 data=countSelectedLocalizations('classic'), 
                 FUN=mean), 
      caption='percentages selected localization trials after classic training')
```

We decided not to use any more outlier removal, but it is implemented and can be switched on in the code: set the `removeOutliers` argument to the `getPointLocalization` function in `shared.R` to TRUE.

## No-cursor selection statistics

Similarly, we get the percentage of selected trials in no-cursor reach tasks in exposure training:

```{r exposure_nocursor_selection}
kable( aggregate(trials ~ 1, 
                 data=countSelectedNoCursors('exposure'), 
                 FUN=mean), 
       caption='percentages selected no-cursor trials after exposure training')
```

And in the classic training group:

```{r classic_nocursor_selection}
kable( aggregate(trials ~ 1, 
                 data=countSelectedNoCursors('classic'), 
                 FUN=mean), 
       caption='percentages selected no-cursor trials after classic training')
```

@@

```{r fig3_localization, fig.width=7.5, fig.height=3}
plotLocalization(selectPerformance=selectPerformance,remove15=FALSE)
```

@@

```{r localization_count_table}
kable(getLocCountTable(selectPerformance=selectPerformance),
      caption='count of participants with localization data at each hand angle')
```

@@

```{r fig2_reachaftereffect, fig.width=7.5, fig.height=3}
plotReachAftereffects(selectPerformance=selectPerformance)
```

@@

There doesn't seem to be an effect of iteration, and no interaction with target. Also, looking at the figure, there would not be decay, as the reach aftereffects seem to get larger. We continue assuming there is no substantial change in the reach aftereffects between the first iteration and the average across the other four iterations. We now also see an effect of target angle: the generalization curve is not flat.

@@

```{r create_svgs, cache=FALSE, include=FALSE}
# This chunk creates SVG files but shouldn't show up in the PDF / HTML 
plotReachAftereffects(generateSVG=TRUE,
                      selectPerformance=selectPerformance)
plotLocalization(classicOnline=FALSE,
                 generateSVG=TRUE, 
                 selectPerformance=selectPerformance)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE, 
                                               selectPerformance=selectPerformance)
```
